---
title: "Covid91 vaccine study Final2020"
author: "Put your name here!"
date: "put the date here"
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(forcats)
OldData <-read.csv(file="covid91.csv",header=TRUE)
#recode aids to say covid and then remove the annoying "X" from the dataframe
FinalData <- OldData %>% mutate(infected = recode(infected, aids = "covid", none = "OK" )) %>% select(-one_of("X"))
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

A new  preventative vaccine (covid91) is under test in clinical trials. Given the nature of this vaccine it is suspected that the drug may exhibit different effectiveness across the variety of subpopulations tracked. Consider population subgroups by gender( guys and gals), drug use, and sexual orientation. Write a complete report that separately considers this drug for each subgroup and your recommendations as to whether people in the subgroup should take the vaccine.

# Females 
```{r}
DataF<-filter(FinalData,sex=="gal")
```


## Graphical Results for Females 
```{r}
barchartGC(~infected + treatment,data=DataF)
barchartGC(~infected + treatment,data=DataF, type="percent")

```

## Numerical Results for Females 

```{r}
table1 <- xtabs(~infected + treatment,data=DataF)
rowPerc(table1)
colPerc(table1)
```

## Inferentials Results for Females 


# Males 

```{r}
DataM<-filter(FinalData,sex=="guy")
```

## Graphical Results for Males 
```{r}
barchartGC(~infected + treatment,data=DataM)
barchartGC(~infected + treatment,data=DataM, type="percent")

```

## Numerical Results for Males

```{r}
table1 <- xtabs(~infected + treatment,data=DataM)
rowPerc(table1)
colPerc(table1)
```

## Inferentials Results for Males

# LGBTQ

```{r}
DataLGBTQ<-filter(FinalData,LGBTQ=="gay")
```

## Graphical Results for LGBTQ 
```{r}
barchartGC(~infected + treatment,data=DataLGBTQ)
barchartGC(~infected + treatment,data=DataLGBTQ, type="percent")

```

## Numerical Results for LGBTQ

```{r}
table1 <- xtabs(~infected + treatment,data=DataLGBTQ)
rowPerc(table1)
colPerc(table1)
```

## Inferentials Results for LGBTQ

# Drug Users 

```{r}
Datadrug<-filter(FinalData,DrugUser=="yes")
```
## Graphical Results for Drug Users  
```{r}
barchartGC(~infected + treatment,data=Datadrug)
barchartGC(~infected + treatment,data=Datadrug, type="percent")

```
## Numerical Results for Drug Users  

```{r}
table1 <- xtabs(~infected + treatment,data=Datadrug)
rowPerc(table1)
colPerc(table1)
```

## Inferentials Results for Drug Users 

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
