---
title: "Covid91 vaccine study Final2020"
author: "Karen Hernandez!"
date: "November 23, 2020"
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(forcats)
OldData <-read.csv(file="covid91.csv",header=TRUE)
#recode aids to say covid and then remove the annoying "X" from the dataframe
FinalData <- OldData %>% mutate(infected = recode(infected, aids = "covid", none = "OK" )) %>% select(-one_of("X"))
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

A new  preventative vaccine (covid91) is under test in clinical trials. Given the nature of this vaccine it is suspected that the drug may exhibit different effectiveness across the variety of subpopulations tracked. Consider population subgroups by gender( guys and gals), drug use, and sexual orientation. Write a complete report that separately considers this drug for each subgroup and your recommendations as to whether people in the subgroup should take the vaccine.

# Females 

```{r}
DataF<-filter(FinalData,sex=="gal")
```


## Graphical Results for Females 

```{r}
barchartGC(~infected + treatment,data=DataF)
barchartGC(~infected + treatment,data=DataF, type="percent")

```

This barchart shows that from the females that got COVID, about 35% took the drug while 65% took the placebo. Which shows that the drug seems to be effective for females. For those females that were not infected, the amount who took the drug was about the same than those who took the placebo. 


## Numerical Results for Females 

```{r}
table1 <- xtabs(~infected + treatment,data=DataF)
rowPerc(table1)
colPerc(table1)
```
The numerical results show that of the female population who were infected, 33.11 % took the drug while 66.89% took the placebo. Of the females that did not get COVID, 50.31% took the drug, while 49.69% took the placebo. This supports our observation of the graph that the drug is working for females. 


## Inferentials Results for Females 

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```

The Fisher's Exact Test shows a very small P value. The 95% confidence interval is between 0.40 and 0.58. The odds ratio is .49:1. This means females who took the drug are about 50% less likely to get infected than those who took the placebo. This means that the drug is working for the females. I would highly recommend the drug for the females.

# Males 

```{r}
DataM<-filter(FinalData,sex=="guy")
```

## Graphical Results for Males 

```{r}
barchartGC(~infected + treatment,data=DataM)
barchartGC(~infected + treatment,data=DataM, type="percent")

```

The barchart shows that from the Males that got COVID, about 58% took the drug compared to about 42% that took the placebo. This means that the drug does not seem to be effective in preventing males from getting infected. For those Males that did not get COVID, about 48% took the drug and 52% took the placebo. 

## Numerical Results for Males

```{r}
table1 <- xtabs(~infected + treatment,data=DataM)
rowPerc(table1)
colPerc(table1)
```
The numerical Results show that of the Males who got COVID, 58.16% took the drug while 41.84% took the placebo. Of those that did not get COVID, 48.54% took the drug, while 51.46% took the placebo. This supports our observations from the graph that the drug is not effective in preventing males from getting infected. 

## Inferentials Results for Males

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```
The fisher's exact test shows a p value of 0.0005801. the 95% confidence interval is between 1.17 and 1.84. The odds ration of 1.47 shows that men are about 1.5 more likely to get infected by taking the drug than those who took the placebo. This means that the drug is not working for the men. Men are about on and a half times more likely to get COVID by taking the drug. My recommendation for men is not to take the drug. 


# LGBTQ

```{r}
DataLGBTQ<-filter(FinalData,LGBTQ=="gay")
```

## Graphical Results for LGBTQ 

```{r}
barchartGC(~infected + treatment,data=DataLGBTQ)
barchartGC(~infected + treatment,data=DataLGBTQ, type="percent")

```

As we can see by the graph, it shows that out of the LGBTQ who got COVID, about 70% took the drug while 30% took the placebo. This shows that the drug is not effective in preventing LGBTQ from getting infected. Of those that did not get COVID, about 49% took the drug and 51% took the placebo. 

## Numerical Results for LGBTQ

```{r}
table1 <- xtabs(~infected + treatment,data=DataLGBTQ)
rowPerc(table1)
colPerc(table1)
```

The Numerical Results for LGBTQ shows that of those who got COVID, 70.69% took the drug while 29.31% took the placebo. Of those that did not get COVID, 49.17% took the drug while 50.83% took the placebo. This proves that our observations from the graphical results that the drug is not effective for the LGBTQ community. 

## Inferentials Results for LGBTQ

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```

In the Fisher's Exact Test, it shows a P value of 0.000005741. The 95% confidence interval is between 1.63 and 3.87. The odds ratio of 2.49:1 shows that for a member of the LGBTQ community, the odds of getting infected are about 2.5 times higher by taking the drug than by taking the placebo. This means that the drug is absolutely not working. The chances of getting COVID are multiplied by two and a half times when taking the drug than by not taking the drug. My recommendation would be to not take the drug. 

# Drug Users 

```{r}
Datadrug<-filter(FinalData,DrugUser=="yes")
```

## Graphical Results for Drug Users  

```{r}
barchartGC(~infected + treatment,data=Datadrug)
barchartGC(~infected + treatment,data=Datadrug, type="percent")

```

We can see that the graph reflects that for the drug users who got COVID, about 35% took the drug while 65% took the placebo. This shows that the drug seems to be working for the drug users. Of those that did not get COVID, about 47% took the drug while 53% took the placebo. 

## Numerical Results for Drug Users  

```{r}
table1 <- xtabs(~infected + treatment,data=Datadrug)
rowPerc(table1)
colPerc(table1)
```

The numerical Results shows that for the drug users who got COVID, only 33.33% took the drug while 66.67% took the placebo. Of those that did not get COVID, 47.83% got the drug while 52.17% got the placebo. This proves that by our observations that the drug is working for the drug users in preventing infection.

## Inferentials Results for Drug Users 


```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```


The Fisher's Exact Test show that the value of P is 0.002273. The 95% confidence interval is between .35 and .81. Tha odds ration of .55:1 means that the drug users are 55% less likely to get infected by taking the drug than those who took the placebo. This means the drug is working and is decreasing the chances of them getting COVID by a little more than half. I would recommend to take the drug. 

# Discussion and Conclusion

I would recommend that if you are female that you take the drug to prevent getting infected. By taking the drug you are 50% less likely to get infected than if you take the placebo.

If you are a male, I would recommend for you to take the drug. By taking the drug you are about 1.5 time more likely to get infected than by taking the placebo. 

If you are a member of the LGBTQ, I would recommend that you take the drug. By taking the drug you are about 2.5 times more likely to get infected than by taking the placebo. 

If you are a drug user, I would recommend that you take the drug. By taking the drug, you are about 55% less likely to get infected than by taking the placebo.

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
